Beating Simple Backtracking Search in Subgraph Algorithms\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/026842/1 and EP/M508056/1].}

### 2018-11-27 paper/paper.tex
Exciting

\Cref{figure:parallel} shows how this scheme performs in practice. Sequentially, we can solve 14,357
instances within the thousand second timeout, with the last instance being solved at 939.0 seconds.
Using thirty six threads on machines with two eighteen core processors, we can solve 14,357
instances with a timeout of only 74.2 seconds, giving an aggregate speedup of 12.7.

@@

\begin{figure}[tb]
    \centering
    \includegraphics{gen-graph-mcs.pdf}

>>>>

\Cref{figure:parallel} shows how this scheme performs in practice. Sequentially, we can solve 14,357
instances within the thousand second timeout, with the last instance being solved at 939.0 seconds.
Using thirty six threads on machines with two eighteen core processors, we can solve 14,357
instances with a timeout of only 74.2 seconds, giving an aggregate speedup
\cite{DBLP:conf/cpaior/HoffmannMNPRS018} of 12.7.

@@

\begin{figure}[tb]
    \includegraphics{gen-graph-mcs.pdf}
